Music Perception 2: Analysis

### 2022-02-02 experiment-1/analysis/analysis.Rmd
add some diagnosis for multi regression
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Articulation (***)
```{r, echo = TRUE}
# normality check
ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
ioi_art_norm_performance <- shapiro.test(ioi[Skill == "articulation"]$Mean)

@@

## Dynamics (**)
```{r, echo = TRUE}
# normality check
ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)

@@

## Articulation (***)
```{r, echo = TRUE}
# normality check
ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
ioi_art_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)

@@

## Dynamics (**)
```{r, echo = TRUE}
# normality check
ioi_dyn_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
ioi_dyn_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)

@@

## Articulation (n.s.)
```{r, echo = TRUE}
# normality check
cv_art_norm_teaching <- shapiro.test(cv[Skill == "articulation"]$Teaching)
cv_art_norm_performance <- shapiro.test(cv[Skill == "articulation"]$CV)

@@

## Dynamics (n.s.)
```{r, echo = TRUE}
# normality check
cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
cv_dyn_norm_performance <- shapiro.test(cv[Skill == "dynamics"]$CV)

@@

## Legato (**)
```{r, echo = TRUE}
# normality check
kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
kot_leg_norm_performance <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)

@@

## Staccato (***)
```{r, echo = TRUE}
# normality check
kot_sta_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
kot_sta_norm_performance <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)

@@

## Forte (n.s.)
```{r, echo = TRUE}
# normality check
kot_for_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
kot_for_norm_performance <- shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)

@@

## Piano (n.s.)
```{r, echo = TRUE}
# normality check
kot_pia_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
kot_pia_norm_performance <- shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)

@@

## Forte (***)
```{r, echo = TRUE}
# normality check
vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
vel_for_norm_performance <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)

@@

## Piano (n.s.)
```{r, echo = TRUE}
# normality check
vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
vel_pia_norm_performance <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)

@@

## Legato (n.s.)
```{r, echo = TRUE}
# normality check
vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
vel_leg_norm_performance <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)

@@

## Staccato (n.s.)
```{r, echo = TRUE}
# normality check
vel_sta_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
vel_sta_norm_performance <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)

@@

## Forte to Piano (***)
```{r, echo = TRUE}
# normality check
vel_diff_ftop_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
vel_diff_ftop_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)

@@

## Piano to Forte (***)
```{r, echo = TRUE}
# normality check
vel_diff_ptof_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
vel_diff_ptof_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)

@@

## Legato to Staccato (n.s.)
```{r, echo = TRUE}
# normality check
vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
vel_diff_ltos_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)

@@

```{r kot-partial-leg, echo = TRUE}
pcor.test(partial[Subcomponent == "Legato"]$KOT, partial[Subcomponent == "Legato"]$Teaching, partial[Subcomponent == "Legato", c("IOI", "KV", "KVDiff")])
```

@@

```{r kot-partial-sta, echo = TRUE}
pcor.test(partial[Subcomponent == "Staccato"]$KOT, partial[Subcomponent == "Staccato"]$Teaching, partial[Subcomponent == "Staccato", c("IOI", "KV", "KVDiff")])
```

@@

```{r vel-partial-for, echo = TRUE}
pcor.test(partial[Subcomponent == "Forte"]$KV, partial[Subcomponent == "Forte"]$Teaching, partial[Subcomponent == "Forte", c("IOI", "KOT", "KVDiff")])
```

@@

```{r vel-partial-pia, echo = TRUE}
pcor.test(partial[Subcomponent == "Piano"]$KV, partial[Subcomponent == "Piano"]$Teaching, partial[Subcomponent == "Piano", c("IOI", "KOT", "KVDiff")])
```

@@

```{r vel-diff-partial-ftop, echo = TRUE}
pcor.test(partial[Subcomponent2 == "FtoP"]$KVDiff, partial[Subcomponent2 == "FtoP"]$Teaching, partial[Subcomponent2 == "FtoP", c("IOI", "KOT", "KV")])
```

@@

```{r vel-diff-partial-ptof, echo = TRUE}
pcor.test(partial[Subcomponent2 == "PtoF"]$KVDiff, partial[Subcomponent2 == "PtoF"]$Teaching, partial[Subcomponent2 == "PtoF", c("IOI", "KOT", "KV")])
```

@@

## Legato
```{r, echo = TRUE}
m1 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Legato"])
summary(m1)
check_model(m1)
```

## Staccato
```{r, echo = TRUE}
m2 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Staccato"])
summary(m2)
check_model(m2)
```

## Forte
```{r, echo = TRUE}
m3 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Forte"])
summary(m3)
check_model(m3)
```

## Piano
```{r, echo = TRUE}
m4 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Piano"])
summary(m4)
check_model(m4)
```

>>>>

## Articulation (***)
```{r, echo = FALSE}
# normality check
ioi_art_norm_teaching <- shapiro.test(ioi[Skill == "articulation"]$Teaching)
ioi_art_norm_performance <- shapiro.test(ioi[Skill == "articulation"]$Mean)

@@

## Dynamics (**)
```{r, echo = FALSE}
# normality check
ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)

@@

## Articulation (***)
```{r, echo = FALSE}
# normality check
ioi_art_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
ioi_art_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "articulation"]$Mean)

@@

## Dynamics (**)
```{r, echo = FALSE}
# normality check
ioi_dyn_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
ioi_dyn_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)

@@

## Articulation (n.s.)
```{r, echo = FALSE}
# normality check
cv_art_norm_teaching <- shapiro.test(cv[Skill == "articulation"]$Teaching)
cv_art_norm_performance <- shapiro.test(cv[Skill == "articulation"]$CV)

@@

## Dynamics (n.s.)
```{r, echo = FALSE}
# normality check
cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
cv_dyn_norm_performance <- shapiro.test(cv[Skill == "dynamics"]$CV)

@@

## Legato (**)
```{r, echo = FALSE}
# normality check
kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
kot_leg_norm_performance <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)

@@

## Staccato (***)
```{r, echo = FALSE}
# normality check
kot_sta_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
kot_sta_norm_performance <- shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)

@@

## Forte (n.s.)
```{r, echo = FALSE}
# normality check
kot_for_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
kot_for_norm_performance <- shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)

@@

## Piano (n.s.)
```{r, echo = FALSE}
# normality check
kot_pia_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
kot_pia_norm_performance <- shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)

@@

## Forte (***)
```{r, echo = FALSE}
# normality check
vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
vel_for_norm_performance <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)

@@

## Piano (n.s.)
```{r, echo = FALSE}
# normality check
vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
vel_pia_norm_performance <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)

@@

## Legato (n.s.)
```{r, echo = FALSE}
# normality check
vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
vel_leg_norm_performance <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)

@@

## Staccato (n.s.)
```{r, echo = FALSE}
# normality check
vel_sta_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
vel_sta_norm_performance <- shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)

@@

## Forte to Piano (***)
```{r, echo = FALSE}
# normality check
vel_diff_ftop_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
vel_diff_ftop_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)

@@

## Piano to Forte (***)
```{r, echo = FALSE}
# normality check
vel_diff_ptof_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
vel_diff_ptof_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)

@@

## Legato to Staccato (n.s.)
```{r, echo = FALSE}
# normality check
vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
vel_diff_ltos_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)

@@

```{r kot-partial-leg, echo = FALSE}
pcor.test(partial[Subcomponent == "Legato"]$KOT, partial[Subcomponent == "Legato"]$Teaching, partial[Subcomponent == "Legato", c("IOI", "KV", "KVDiff")])
```

@@

```{r kot-partial-sta, echo = FALSE}
pcor.test(partial[Subcomponent == "Staccato"]$KOT, partial[Subcomponent == "Staccato"]$Teaching, partial[Subcomponent == "Staccato", c("IOI", "KV", "KVDiff")])
```

@@

```{r vel-partial-for, echo = FALSE}
pcor.test(partial[Subcomponent == "Forte"]$KV, partial[Subcomponent == "Forte"]$Teaching, partial[Subcomponent == "Forte", c("IOI", "KOT", "KVDiff")])
```

@@

```{r vel-partial-pia, echo = FALSE}
pcor.test(partial[Subcomponent == "Piano"]$KV, partial[Subcomponent == "Piano"]$Teaching, partial[Subcomponent == "Piano", c("IOI", "KOT", "KVDiff")])
```

@@

```{r vel-diff-partial-ftop, echo = FALSE}
pcor.test(partial[Subcomponent2 == "FtoP"]$KVDiff, partial[Subcomponent2 == "FtoP"]$Teaching, partial[Subcomponent2 == "FtoP", c("IOI", "KOT", "KV")])
```

@@

```{r vel-diff-partial-ptof, echo = FALSE}
pcor.test(partial[Subcomponent2 == "PtoF"]$KVDiff, partial[Subcomponent2 == "PtoF"]$Teaching, partial[Subcomponent2 == "PtoF", c("IOI", "KOT", "KV")])
```

@@

## Legato
```{r, echo = FALSE}
m1 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Legato"])
summary(m1)
check_model(m1)
```

### Collinearity
```{r, echo = FALSE}
check_collinearity(m1)
```

### Heteroscedacity
```{r, echo = FALSE}
check_heteroscedasticity(m1)
```

### Normality
```{r, echo = FALSE}
check_normality(m1)
```

## Staccato
```{r, echo = FALSE}
m2 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Staccato"])
summary(m2)
check_model(m2)
```

### Collinearity
```{r, echo = FALSE}
check_collinearity(m2)
```

### Heteroscedacity
```{r, echo = FALSE}
check_heteroscedasticity(m2)
```

### Normality
```{r, echo = FALSE}
check_normality(m2)
```

## Forte
```{r, echo = FALSE}
m3 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Forte"])
summary(m3)
check_model(m3)
```

### Collinearity
```{r, echo = FALSE}
check_collinearity(m3)
```

### Heteroscedacity
```{r, echo = FALSE}
check_heteroscedasticity(m3)
```

### Normality
```{r, echo = FALSE}
check_normality(m3)
```

## Piano
```{r, echo = FALSE}
m4 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Piano"])
summary(m4)
check_model(m4)
```

### Collinearity
```{r, echo = FALSE}
check_collinearity(m4)
```

### Heteroscedacity
```{r, echo = FALSE}
check_heteroscedasticity(m4)
```

### Normality
```{r, echo = FALSE}
check_normality(m4)
```

### 2022-02-02 experiment-2/analysis/analysis.Rmd
add some diagnosis for multi regression
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# midi
if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
if (!require("qqplotr")) {install.packages("qqplotr"); require("qqplotr")}
# stats
if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
if (!require("performance")) {install.packages("performance"); require("performance")}
```

>>>>

# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# midi
if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
# stats
if (!require("ppcor")) {install.packages("ppcor"); require("ppcor")}
if (!require("performance")) {install.packages("performance"); require("performance")}
```
